Fast Sorting on Modern Computers

### 2005-08-30 docs/tech_report/shell.tex
minor edit on that

A slight difference occurs in the two algorithms. Due to a slight difference
in behaviour when $h = 5$, the improved shellsort runs faster than shellsort
when this condition occurs. This is due to shellsort running an extra iteration,
with $h = 2$, which is skipped by improved shellsort. This occurs when the array
is sized $16,384$, $32,768$ and $4,194,304$.

@@

In general, the number of taken branches in both sorts would be almost exactly
the same, with only a minor difference due to the positioning of the sentinel.
However, during the sorts, the $h = 5$ condition was hit, meaning that there
were less branches and less taken branches in the improved shellsort, than in
the shellsort.

The results show that in improved shellsort, each key moves an average 0.915
places each iteration, while in the final insertion sort, each key moves an
average of 2.1 places. We can extrapolate a weighted average from this, to
determine that in shellsort, run under the same conditions, each key would move
an average of 0.9744.

>>>>

Apart from these changes, the two algorithms algorithms are subtly different.
Due to a slight difference in behaviour when $h = 5$, the improved shellsort
runs faster than shellsort when this condition occurs. This is due to shellsort
running an extra iteration, with $h = 2$, which is skipped by improved
shellsort. This occurs when the array is sized 16384, 32768 and 4194304.

@@

In general, the number of taken branches in both sorts would be almost exactly
the same, with only a minor difference due to the positioning of the sentinel.
However, during the sorts, the $h = 5$ condition was hit, meaning that there
were less branches and less taken branches in the improved shellsort than in the
shellsort.

The results show that in improved shellsort, each key moves an average 0.915
places each iteration, while in the final insertion sort, each key moves an
average of 2.1 places. We can extrapolate a weighted average from this, to
determine that in shellsort, run under the same conditions, each key would move
an average of 0.9744 places.
